Ao's Notes on Medical Imaging Software

### 2020-04-30 StateOfPractice/Ao-Notes/Ao-Notes.tex
update notes

>>>>

\section{Questions to Domain Experts}

\subsection{Software}
\begin{itemize}
\item What do you think of our process of selecting software candidates?
\item What do you think of the list of the selected software?
\item Is there any software you think should be removed from / added to the
list?
\end{itemize}

\subsection{Schedule}
\begin{itemize}
\item We propose to start this project from ... and finish it before ... . What
do you think?
\item Our meeting schedule
\end{itemize}

\subsection{Team}
\begin{itemize}
\item How many members do you think will be in the team for analyzing this
domain?
\item How many hours can a team member commit?
\item Is there any other experts you think we should keep them involved?
\end{itemize}

\subsection{Technical}
\begin{itemize}
\item Equipment such as computers, test tools, OS
\item Technical details such as screen recording, questionnaires.
\end{itemize}
